Consistent Polyhedral Surrogates via Embedding

### 2019-05-16 notes/bo-separated.tex
improving proofs in bo-separated

Let some norm $\|\cdot\|$ on finite-dimensional Euclidean space is given.
Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.

@@

\bo{This is embarassing, but I don't have a citation for this lemma so I wrote a hacky, but I think correct, proof.}
\begin{lemma} \label{lemma:open-plus-closed-poly}
  If $D$ is a closed convex polyhedron (the intersection of finitely many closed halfspaces) and $S'$ is an open polyhedron (the intersection of finitely many open halfspaces), then $D+S'$ is an open polyhedron.
\end{lemma}
\begin{proof}
  Let $\bar{D}$ be the closure of $D$ and let $\text{bo}(D)$ be the boundary of $D$.

  By standard results, $D + \bar{S'}$ is a closed polyhedron.
  Furthermore, we claim (1) that $D + S'$ is an open set and (2) that $\bar{D + S'} = D + \bar{S'}$.
  This proves the lemma, because $D+S'$ is the open set whose closure is the closed polyhedron $D + \bar{S'}$.

  To prove (1), let $z \in D + S'$ with $z=x+y, x \in D, y \in S'$.
  Because $S'$ is open, there is some $B(y,\epsilon) \subseteq S'$, so $D+S'$ contains $B(z,\epsilon) = \{x\} + B(y,\epsilon)$, so $z$ is not a boundary point.
  We have shown $D + S'$ does not contain any boundary points, so it is open.

  To prove (2), we must show containment in both directions.
  Let $z \in \bar{D+S'}$.
  If $z$ is in the interior, then $z \in D+S'$, so $z \in D + \bar{S'}$.
  Let $z \in \text{bo}(D+S')$.
  \bo{TODO}
\end{proof}

\begin{lemma} \label{lemma:enclose-halfspaces}
  Let $D$ be a closed, convex polyhedron in $\reals^d$.
  For any $\epsilon > 0$, there exists a convex set $D'$, the intersection of a finite number of open halfspaces, such that
    \[ D \subsetneq D' \subsetneq B(D,\epsilon) . \]
\end{lemma}
\begin{proof}
  Let $S$ be the standard $\epsilon$-ball $B(\{\vec{0}\},\epsilon)$.
  Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
  Now let $S' = \{u : \|u\|_1 < \delta\}$ be the open $\delta$ ball in $L_1$ norm.
  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subsetneq S$.
  By Lemma \ref{lemma:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.

  Now, if $T' \subsetneq T$, and the sets $T',T,D$ are convex and not equal to the whole of $\reals^d$, then the Minkowksi sum satisfies $D + T' \subsetneq D + T$.
  \bo{TODO - separate into a lemma as well?}
  In particular, because $\emptyset \subsetneq S' \subsetneq S$, we have
    \[ D \subsetneq D' \subsetneq B(D,\epsilon) . \]
  Now we observe that because $D'$ is a polyhedron, we can write it as the intersection of a finite number of halfspaces, which we can make open sets.\bo{Ought to improve/reword this.}
\end{proof}

\begin{lemma} \label{lemma:thick-nonempty}
  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets with nonempty joint intersection.
  Then for all $\delta > 0$, there exists  $\epsilon > 0$ such that $\cap_j B(U_j,\epsilon) = \subseteq B(\cap_j U_j, \delta)$.
\end{lemma}
\begin{proof}
  By induction on the size of the collection.
  If the size is $1$, set $\epsilon = \delta$.
  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
  Let $D = U_j \cap U'$.
  We must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D,\delta)$.
  By Lemma \ref{lemma:enclose-halfspaces}, we can enclose $D$ strictly within a polyhedron $D'$, the intersection of a finite number of open halfspaces, which is itself strictly enclosed in $B(D,\delta)$.
  For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D,\delta)$.
%  \raf{We can use the fact that the $U_j$ are all polyhedral here, so $D$ is polyhedral as well.  Now let $B_1()$ be a ball with respect to $\|\cdot\|_1$, and observe that $B_1(D,\delta')$ is therefore also polyhedral for all $\delta'$.  Using norm bounds, we can find a small enough $\delta'$ so that $B_1(D,\delta') \subseteq B(D,\delta)$.}
  We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in $D'$.
  This implies that it is contained in $B(D,\delta)$.

>>>>

Let some norm $\|\cdot\|$ on finite-dimensional Euclidean space be given.
Given a set $T$ and a point $u$, let $d(T,u) = \inf_{t \in T} \|t-u\|$.

@@

\begin{lemma} \label{lemma:enclose-halfspaces}
  Let $D$ be a closed, convex polyhedron in $\reals^d$.
  For any $\epsilon > 0$, there exists an open, convex polyhedron $D'$, the intersection of a finite number of open halfspaces, such that
    \[ D \subseteq D' \subseteq B(D,\epsilon) . \]
\end{lemma}
\begin{proof}
  Let $S$ be the standard $\epsilon$-ball $B(\{\vec{0}\},\epsilon)$.
  Note that $B(D,\epsilon) = D + S$ where $+$ is the Minkowski sum.
%  Now let $S' = \{u : \|u\|_1 < \delta\}$ be the open $\delta$ ball in $L_1$ norm.
%  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
%  By Lemma \ref{lemma:open-plus-closed-poly}, the Minkowski sum $D' = D + S'$ is an open polyhedron, i.e. the intersection of a finite number of open halfspaces.
  Now let $S' = \{u : \|u\|_1 \leq \delta\}$ be the closed $\delta$ ball in $L_1$ norm.
  By equivalence of norms in Euclidean space, \bo{cite} we can take $\delta$ small enough yet positive such that $S' \subseteq S$.
  By standard results, the Minkowski sum of two closed, convex polyhedra, $D'' = D + S'$ is a closed polyhedron, i.e. the intersection of a finite number of closed halfspaces.\footnote{A proof: we can form the higher-dimensional polyhedron $\{(x,y,z) : x \in D, y \in S', z = x+y\}$, then project onto the $z$ coordinates.}

  Now, if $T' \subseteq T$, then the Minkowksi sum satisfies $D + T' \subseteq D + T$.
  In particular, because $\emptyset \subseteq S' \subseteq S$, we have
    \[ D \subseteq D'' \subseteq B(D,\epsilon) . \]
  Now let $D'$ be the interior of $D''$, i.e. if $D'' = \{x : Ax \leq b\}$, then we let $D' = \{x: Ax < b\}$.
  We retain $D' \subseteq B(D,\epsilon)$.
  Further, we retain $D \subseteq D'$, because $D$ is contained in the interior of $D'' = D + S'$.
  (Proof: if $x \in D$, then for some $\gamma$, $x + B(\{\vec{0}\},\gamma) = B(x,\gamma)$ is contained in $D + S'$.)
  This proves the lemma.
\end{proof}

\begin{lemma} \label{lemma:thick-nonempty}
  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets with nonempty joint intersection.
  Then there exists  $\epsilon > 0$ such that $\cap_j B(U_j,\epsilon) \subseteq B(\cap_j U_j, \delta)$.
\end{lemma}
\begin{proof}
  By induction on the size of the collection.
  If the size is $1$, set $\epsilon = \delta$.
  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
  Let $D = U_j \cap U'$.
  We must show that $B(U_j,\epsilon) \cap C(\epsilon) \subseteq B(D,\delta)$.
  By Lemma \ref{lemma:enclose-halfspaces}, we can enclose $D$ strictly within a polyhedron $D'$, the intersection of a finite number of open halfspaces, which is itself strictly enclosed in $B(D,\delta)$.
  For example, if $D$ is a point, then enclose it in a hypercube, which is enclosed in the ball $B(D,\delta)$.
%  \raf{We can use the fact that the $U_j$ are all polyhedral here, so $D$ is polyhedral as well.  Now let $B_1()$ be a ball with respect to $\|\cdot\|_1$, and observe that $B_1(D,\delta')$ is therefore also polyhedral for all $\delta'$.  Using norm bounds, we can find a small enough $\delta'$ so that $B_1(D,\delta') \subseteq B(D,\delta)$.}
  We will prove that, for small enough $\epsilon$, $B(U_j,\epsilon) \cap C(\epsilon)$ is contained in $D'$.
  This implies that it is contained in $B(D,\delta)$.
